Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-12-29 grove-paper.tex
add some text on graph decomposition

>>>>

Graph decomposition occurs in three steps.

First, a linear scan is performed over every edge that has been created or
deleted. The vertices at both ends are partitioned into three sets:
multi-parented, single-parented, or orphaned. Maps for O($\log n$) parent and
child edge set lookups are also created.

Second, the subgraphs rooted at vertices with more or less than one parent are
traversed and equivalent tree structures are generated over components that are
connected by single-parented vertices. Cycles are broken with UUID vertex
references. Single-parented vertices reachable from the root vertex are also
traversed.

Finally, any remaining single-parented vertices are parts of wreaths. A wreath
is a cycle of single-parented vertices that each may have single-parented
descendants.

Wreath traversal occurs in two directions. A vertex is chosen as an arbitrary
starting point and its parents are traversed and marked as seen. Any vertex that
has been seen twice must be on the cycle. We take the first one as the root of
the wreath and traverse its children to produce a tree that covers the wreath.
Any remaining single-parented vertices must be parts of other wreaths and are
wreath-traversed until there are no more single-parented vertices left.
